---
title: "Conners' param recov"
author: "Andreas"
date: "2025-01-14"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


Load packages
```{r}
library(pacman)
pacman::p_load(tidyverse, cmdstanr, posterior, ggridges, patchwork)

# defining a function for calculating the maximum of the posterior density (not exactly the same as the mode)
MPD <- function(x) {
  density(x)$x[which(density(x)$y==max(density(x)$y))]
}

z <- function(x) {
  return( (x-mean(x))/sd(x) )
}
```


Load data simulation function
```{r}
source("C:/Users/andre/OneDrive - Aarhus universitet/Cognitive Science/Kandidat/Speciale/Analysis/simulation_functions/Conners_TGM_sim_f.R")
ntrials <- 360
ntargets <- 324

nconditions <- 1
```


Compile Stan model
```{r}
file <- file.path("C:/Users/andre/OneDrive - Aarhus universitet/Cognitive Science/Kandidat/Speciale/Analysis/Task_specific_models/conners_diffusion_model.stan")

wiener_conners_mod = cmdstan_model(file)
```


Simulate a single session

```{r}
# Set parameter values
a <- 1.2
b <- 0.5
v <- 2
t <- 0.2
FA <- - 1
d <- c(0) # Only one condition, so no difficulty effect.
w <- 0 # and nothing to adapt to

# Simulate data
sim_data1 <- Conners_TGM_sim_f(ntrials, ntargets, v, a, b, t, d, FA, w)

# Look at the simulated data

plot(density(sim_data1$RT[sim_data1$button_pressed == 1 & sim_data1$correct == 1]), main = "RTs (Correct trials)")
plot(density(sim_data1$RT[sim_data1$button_pressed == 1 & sim_data1$correct == 0]), main = "RTs (Incorrect trials)")


```


Set priors
```{r}
a_prior_m <- 0
a_prior_sd <- 1
b_prior_m <- 0
b_prior_sd <- 1
v_prior_m <- 0
v_prior_sd <- 1
t_prior_m <- 0
t_prior_sd <- 1
FA_prior_m <- 0
FA_prior_sd <- 1

```



Fit Stan model
```{r}
# Prepare data for Stan

ncorrectRTs <- length(sim_data1$RT[sim_data1$RT > 0 & sim_data1$correct == 1])
nincorrectRTs <- length(sim_data1$RT[sim_data1$RT > 0 & sim_data1$correct == 0])

min_rt <- min(sim_data1$RT[sim_data1$RT > 0])


data <- list(ntrials = ntrials,
             button_pressed = sim_data1$button_pressed,
             target_present = sim_data1$target_present,
             correct = sim_data1$correct,
             RT = sim_data1$RT,
             falsealarm = sim_data1$FA_trial,
             ncorrectRTs = ncorrectRTs,
             nincorrectRTs = nincorrectRTs,
             min_rt = min_rt,
             
             a_prior_m = a_prior_m,
             a_prior_sd = a_prior_sd,
             b_prior_m = b_prior_m,
             b_prior_sd = b_prior_sd,
             v_prior_m = v_prior_m,
             v_prior_sd = v_prior_sd,
             t_prior_m = t_prior_m,
             t_prior_sd = t_prior_sd,
             FA_prior_m = FA_prior_m,
             FA_prior_sd = FA_prior_sd
             )
```

```{r}
# Start sampling
samples <- wiener_conners_mod$sample(
  data = data,
  seed = 123,
  chains = 3,
  parallel_chains = 3,
  iter_warmup = 1000,
  iter_sampling = 3000,
  refresh = 500,
  max_treedepth = 10,
  adapt_delta = 0.99
)

draws_df <- as_draws_df(samples$draws())


```

Visualize the model fit
```{r}

# Prior Posterior Update checks

p1 <- draws_df %>% ggplot() +
  geom_density(aes(log_a), fill = "red", alpha = 0.3) +
  geom_density(aes(log_a_prior), fill = "blue", alpha = 0.3) +
  theme_minimal()

p2 <- draws_df %>% ggplot() +
  geom_density(aes(a), fill = "red", alpha = 0.3) +
  geom_density(aes(a_prior), fill = "blue", alpha = 0.3) +
  geom_point(x = a, y = -0.1) +
  xlim(0, 5) +
  theme_minimal()

p3 <- draws_df %>% ggplot() +
  geom_density(aes(logit_b), fill = "red", alpha = 0.3) +
  geom_density(aes(logit_b_prior), fill = "blue", alpha = 0.3) +
  theme_minimal()

p4 <- draws_df %>% ggplot() +
  geom_density(aes(b), fill = "red", alpha = 0.3) +
  geom_density(aes(b_prior), fill = "blue", alpha = 0.3) +
  geom_point(x = b, y = -0.1) +
  theme_minimal()

p5 <- draws_df %>% ggplot() +
  geom_density(aes(cont_t), fill = "red", alpha = 0.3) +
  geom_density(aes(cont_t_prior), fill = "blue", alpha = 0.3) +
  theme_minimal()

p6 <- draws_df %>% ggplot() +
  geom_density(aes(t), fill = "red", alpha = 0.3) +
  geom_density(aes(t_prior), fill = "blue", alpha = 0.3) +
  geom_point(x = t, y = -0.1) +
  xlim(0,0.35) +
  theme_minimal()

p7 <- draws_df %>% ggplot() +
  geom_density(aes(log_v), fill = "red", alpha = 0.3) +
  geom_density(aes(log_v_prior), fill = "blue", alpha = 0.3) +
  theme_minimal()

p8 <- draws_df %>% ggplot() +
  geom_density(aes(v), fill = "red", alpha = 0.3) +
  geom_density(aes(v_prior), fill = "blue", alpha = 0.3) +
  geom_point(x = v, y = -0.05) +
  xlim(0,5) +
  theme_minimal()

p9 <- draws_df %>% ggplot() +
  geom_density(aes(log_FA), fill = "red", alpha = 0.3) +
  geom_density(aes(log_FA_prior), fill = "blue", alpha = 0.3) +
  theme_minimal()

p10 <- draws_df %>% ggplot() +
  geom_density(aes(FA), fill = "red", alpha = 0.3) +
  geom_density(aes(FA_prior), fill = "blue", alpha = 0.3) +
  geom_point(x = - FA, y = -0.05) +
  xlim(0,5) +
  theme_minimal()

(p1 + p2) / (p3 + p4) / (p5 + p6) / (p7 + p8) / (p9 + p10)

```

PP Checks

```{r}

source("C:/Users/andre/OneDrive - Aarhus universitet/Cognitive Science/Kandidat/Speciale/Analysis/visualization_functions/wiener_ppcheck.R")

correct_RTs <- sim_data1$RT[sim_data1$button_pressed == 1 & sim_data1$correct == 1]

# Prior preds of RTs
wiener_ppcheck(correct_RTs, draws_df, prior_only = TRUE, nconditions = nconditions, n_draws = 100)

# Posterior preds RTs
wiener_ppcheck(correct_RTs, draws_df, prior_only = FALSE, nconditions = nconditions, n_draws = 100)


```


Check Chains
```{r}
draws_df %>% mutate(chain = as.factor(.chain)) %>%  ggplot() +
  geom_line(aes(x = .iteration, y = log_a, color = chain))

draws_df %>% mutate(chain = as.factor(.chain)) %>%  ggplot() +
  geom_line(aes(x = .iteration, y = logit_b, color = chain))

draws_df %>% mutate(chain = as.factor(.chain)) %>%  ggplot() +
  geom_line(aes(x = .iteration, y = cont_t, color = chain))

draws_df %>% mutate(chain = as.factor(.chain)) %>%  ggplot() +
  geom_line(aes(x = .iteration, y = log_v, color = chain))

draws_df %>% mutate(chain = as.factor(.chain)) %>%  ggplot() +
  geom_line(aes(x = .iteration, y = log_FA, color = chain))

```


True parameters and simulated data will be read in, so we use the same data all the way through

```{r}
true_params <- read.csv("draws_and_true_params/TGM_fixed_d_and_SD_true_params_2025-03-10_125332.675184.csv")
ntrials_pr_task <- c(450, 360, 300) # CPT-IP, Conners', RVP
nconditions_pr_task <- c(3, 1, 1)
ntargets_pr_task <- c(90, 324, 24)
ntasks <- 3
d <- array(c(0.5,2,4,
             0.1,NA,NA,
             1,NA,NA), dim = c(ntasks, max(nconditions_pr_task)))
conners_d <- d[1,2]

sim_dat <- read.csv("TGM_fixed_d_and_SD_sim_dat_2025-03-10_125332.675184.csv")
```


Setup parameter recovery

```{r}
niter <- 30
nchains <- 3
nsamples <- 3000

# true_a <- array(NA, niter)
# true_b <- array(NA, niter)
# true_v <- array(NA, niter)
# true_t <- array(NA, niter)

infer_a <- array(NA, dim = c(niter, nchains*nsamples))
infer_b <- array(NA, dim = c(niter, nchains*nsamples))
infer_v <- array(NA, dim = c(niter, nchains*nsamples))
infer_t <- array(NA, dim = c(niter, nchains*nsamples))
infer_FA <- array(NA, dim = c(niter, nchains*nsamples))

for (i in 1:niter){
  print(paste("ITERATION", i))
  
  # sample parameter values
  # a <- runif(1, 0.5, 3)
  # b <- runif(1, 0.3, 0.7)
  # v <- runif(1, 0.5, 3)
  # t <- runif(1, 0.100, 0.250)
  # 
  # true_a[i] <- a
  # true_b[i] <- b
  # true_v[i] <- v
  # true_t[i] <- t
  
  
  # Simulate data
  # sim_data <- CPT_w_difficulties_wiener_sim_f(ntrials, ntargets, v, a, b, t, d)
  sim_data <- sim_dat %>% filter(ID == i & task_name == "Conners")
  
  # Prepare data for Stan model
  ncorrectRTs <- length(sim_data$RT[sim_data$RT > 0 & sim_data$correct == 1])
  nincorrectRTs <- length(sim_data$RT[sim_data$RT > 0 & sim_data$correct == 0])
  
  min_rt <- min(sim_data$RT[sim_data$RT > 0])

  data <- list(ntrials = ntrials,
               button_pressed = sim_data$button_pressed,
               target_present = sim_data$target_present,
               correct = sim_data$correct,
               RT = sim_data$RT,
               falsealarm = sim_data$FA_trial,
               ncorrectRTs = ncorrectRTs,
               nincorrectRTs = nincorrectRTs,
               min_rt = min_rt,
               
               a_prior_m = a_prior_m,
               a_prior_sd = a_prior_sd,
               b_prior_m = b_prior_m,
               b_prior_sd = b_prior_sd,
               v_prior_m = v_prior_m,
               v_prior_sd = v_prior_sd,
               t_prior_m = t_prior_m,
               t_prior_sd = t_prior_sd,
               FA_prior_m = FA_prior_m,
               FA_prior_sd = FA_prior_sd
               )
  
  # Start sampling
  temp_samples <- wiener_conners_mod$sample(
    data = data,
    seed = 123,
    chains = 3,
    parallel_chains = nchains,
    iter_warmup = 1000,
    iter_sampling = nsamples,
    refresh = 0,
    max_treedepth = 10,
    adapt_delta = 0.99
  )
  
  # Record MPDs of posteriors
  
  infer_a[i,] <- temp_samples$draws(variables = "a")
  infer_b[i,] <- temp_samples$draws(variables = "b")
  infer_v[i,] <- temp_samples$draws(variables = "v")
  infer_t[i,] <- temp_samples$draws(variables = "t")
  infer_FA[i,] <- temp_samples$draws(variables = "FA")
}

```


The true param values:
```{r}
true_a <- true_params$a2
true_b <- true_params$b2
true_v <- true_params$v2
true_t <- true_params$t2
true_FA <- true_params$FA2

# EEA given difficulty d
true_EEA_given_d <- true_v - 0.2 * conners_d
true_EEA_given_d <- ifelse(true_EEA_given_d < 0, 0, true_EEA_given_d)
# Caution given w and d
true_caut <- true_a + true_params$w * 0.2 * conners_d
```



Save recovery data
```{r}
recov_df <- data.frame()
for (i in 1:niter){
  recov_df <- rbind(recov_df, data.frame("param" = "a", "infer" = infer_a[i,], "iteration" = i, "true" = true_a[i]))
  recov_df <- rbind(recov_df, data.frame("param" = "b", "infer" = infer_b[i,], "iteration" = i, "true" = true_b[i]))
  recov_df <- rbind(recov_df, data.frame("param" = "v", "infer" = infer_v[i,], "iteration" = i, "true" = true_v[i]))
  recov_df <- rbind(recov_df, data.frame("param" = "t", "infer" = infer_t[i,], "iteration" = i, "true" = true_t[i]))
  recov_df <- rbind(recov_df, data.frame("param" = "FA", "infer" = infer_FA[i,], "iteration" = i, "true" = true_FA[i]))
}

# write.csv(recov_df, "infer_params_conners_recov_2025-03-10_125332.675184.csv")

recov_df <- read.csv("infer_params_conners_recov_2025-03-10_125332.675184.csv")

recov_summa <- recov_df %>% group_by(param, iteration) %>%
  summarise(infer_mean = mean(infer),
            infer_MPD = MPD(infer),
            ci95up = quantile(infer, probs = c(0.025, 0.975))[2],
            ci95low = quantile(infer, probs = c(0.025, 0.975))[1],
            ci50up = quantile(infer, probs = c(0.25, 0.75))[2],
            ci50low = quantile(infer, probs = c(0.25, 0.75))[1],
            true = mean(true)
            )

recov_summa2 <- recov_df %>% dplyr::select(-true) %>% rename("ID" = iteration) %>% 
  group_by(ID, param) %>%
  summarize(infer_mean = mean(infer)) %>% 
  pivot_wider(names_from = param, values_from = infer_mean)

recov_summa2$true_a <- true_a
recov_summa2$true_b <- true_b
recov_summa2$true_v <- true_v
recov_summa2$true_t <- true_t
recov_summa2$true_FA <- true_FA
recov_summa2$true_caut <- true_caut
recov_summa2$true_EEA_given_d <- true_EEA_given_d
```


Visualize recovery

```{r}
# recov_df %>% filter(param == "a") %>% ggplot() +
#   geom_point(aes(x = true, y = infer), alpha = 1/10) +
#   theme_minimal()
# 
# recov_summa %>% filter(param == "a") %>% ggplot(aes(x = true, y = infer_MPD)) +
#   geom_errorbar(aes(ymin = ci95low, ymax=ci95up, width=0)) +
#   geom_errorbar(aes(ymin = ci50low, ymax=ci50up, width=0), size = 1.1) +
#   geom_point(size = 1.5, color = "darkblue") +
#   geom_abline(slope = 1, intercept = 0, color = "red") +
#   theme_minimal()


recov_summa2 %>% ggplot() +
  geom_point(aes(x = true_a, y = a)) +
  geom_abline(slope = 1, intercept = 0, color = "red") +
  theme_minimal()

recov_summa2 %>% ggplot() +
  geom_point(aes(x = true_b, y = b)) +
  geom_abline(slope = 1, intercept = 0, color = "red") +
  theme_minimal()

recov_summa2 %>% ggplot() +
  geom_point(aes(x = true_v, y = v)) +
  geom_abline(slope = 1, intercept = 0, color = "red") +
  theme_minimal()

recov_summa2 %>% ggplot() +
  geom_point(aes(x = true_t, y = t)) +
  geom_abline(slope = 1, intercept = 0, color = "red") +
  theme_minimal()

recov_summa2 %>% ggplot() +
  geom_point(aes(x = true_FA, y = -FA)) +
  geom_abline(slope = 1, intercept = 0, color = "red") +
  theme_minimal()


library(latex2exp)

recplt_a <- recov_summa2 %>% ggplot() +
  geom_point(aes(x = true_a, y = a)) +
  geom_abline(slope = 1, intercept = 0, color = "red") +
  theme_minimal() +
  labs(title = expression(paste("Recovery of parameter ", italic("a"))),
       x = expression(paste("True ", italic("a"))),
       y = expression(paste("Mean inferred ", italic("a")))) +
  theme(text = element_text(size = 14, family = "serif"))

recplt_b <- recov_summa2 %>% ggplot() +
  geom_point(aes(x = true_b, y = b)) +
  geom_abline(slope = 1, intercept = 0, color = "red") +
  theme_minimal() +
  labs(title = expression(paste("Recovery of parameter ", italic("b"))),
       x = expression(paste("True ", italic("b"))),
       y = expression(paste("Mean inferred ", italic("b")))) +
  theme(text = element_text(size = 14, family = "serif"))

recplt_v <- recov_summa2 %>% ggplot() +
  geom_point(aes(x = true_v, y = v)) +
  geom_abline(slope = 1, intercept = 0, color = "red") +
  theme_minimal() +
  labs(title = expression(paste("Recovery of parameter ", italic("v"))),
       x = expression(paste("True ", italic("v"))),
       y = expression(paste("Mean inferred ", italic("v")))) +
  theme(text = element_text(size = 14, family = "serif"))

recplt_t <- recov_summa2 %>% ggplot() +
  geom_point(aes(x = true_t, y = t)) +
  geom_abline(slope = 1, intercept = 0, color = "red") +
  theme_minimal() +
  labs(title = TeX("Recovery of parameter $\\tau$"),
       x = TeX("True $\\tau$"),
       y = TeX("Mean inferred $\\tau$")) +
  theme(text = element_text(size = 14, family = "serif"))

recplt_FA <- recov_summa2 %>% ggplot() +
  geom_point(aes(x = true_FA, y = -FA)) +
  geom_abline(slope = 1, intercept = 0, color = "red") +
  theme_minimal() +
  labs(title = expression(paste("Recovery of parameter ", italic("FA"))),
       x = expression(paste("True ", italic("FA"))),
       y = expression(paste("Mean inferred ", italic("FA")))) +
  theme(text = element_text(size = 14, family = "serif"))

(recplt_a + recplt_b + recplt_v) / (recplt_t + recplt_FA)

# recov_summa2 %>% ggplot() +
#   geom_point(aes(x = true_caut, y = a)) +
#   geom_abline(slope = 1, intercept = 0, color = "red") +
#   theme_minimal()
# 
# recov_summa2 %>% ggplot() +
#   geom_point(aes(x = true_EEA_given_d, y = v)) +
#   geom_abline(slope = 1, intercept = 0, color = "red") +
#   theme_minimal()
  
```



Preservation of ranking, Fit ordinal regressions

```{r}
library(ordinal)
niter <- 30
true_params <- data.frame(true_a, true_b, true_v, true_t, true_FA, ID = seq(niter))
true_params$rank_a <- rank(true_params$true_a)
true_params$rank_b <- rank(true_params$true_b)
true_params$rank_v <- rank(true_params$true_v)
true_params$rank_t <- rank(true_params$true_t)
true_params$rank_FA <- rank(true_params$true_FA)
ranking_d <- true_params %>% dplyr::select(ID, starts_with("rank"))

draws_df <- data.frame()
for (i in 1:niter){
  temp <- data.frame(a = recov_df$infer[recov_df$param == "a" & recov_df$iteration == i],
                     b = recov_df$infer[recov_df$param == "b" & recov_df$iteration == i],
                     v = recov_df$infer[recov_df$param == "v" & recov_df$iteration == i],
                     t = recov_df$infer[recov_df$param == "t" & recov_df$iteration == i],
                     FA = recov_df$infer[recov_df$param == "FA" & recov_df$iteration == i],
                     ID = i)
  draws_df <- rbind(draws_df, temp)
}

draws_df$FA <- - draws_df$FA # Flip sign of the FA effect


draws_df <- merge(draws_df, ranking_d, by = "ID") # merge rankings with the draws

draws_df$rank_a <- as.factor(draws_df$rank_a)
draws_df$rank_b <- as.factor(draws_df$rank_b)
draws_df$rank_v <- as.factor(draws_df$rank_v)
draws_df$rank_t <- as.factor(draws_df$rank_t)
draws_df$rank_FA <- as.factor(draws_df$rank_FA)

draws_df <- draws_df %>% 
  mutate(
    a_z = z(a),
    b_z = z(b),
    v_z = z(v),
    t_z = z(t),
    FA_z = z(FA)
  )

# Fit models for each param

m_a <- clm(rank_a ~ a_z, data = draws_df)
m_b <- clm(rank_b ~ b_z, data = draws_df)
m_v <- clm(rank_v ~ v_z, data = draws_df)
m_t <- clm(rank_t ~ t_z, data = draws_df)
m_FA <- clm(rank_FA ~ FA_z, data = draws_df)


m_a$coefficients["a_z"]
m_b$coefficients["b_z"]
m_v$coefficients["v_z"]
m_t$coefficients["t_z"]
m_FA$coefficients["FA_z"]

summary(m_a)
summary(m_b)
summary(m_v)
summary(m_t)
summary(m_FA)

```



Mean of absolute errors

```{r}
# a
a_abs_err <- array(NA, dim = dim(infer_a))
for (i in 1:niter){
  a_abs_err[i,] <- abs(infer_a[i,] - true_a[i])
}
a_mean_abs_err <- colMeans(a_abs_err) # Take mean over iterations
plot(density(a_mean_abs_err))


# b
b_abs_err <- array(NA, dim = dim(infer_b))
for (i in 1:niter){
  b_abs_err[i,] <- abs(infer_b[i,] - true_b[i])
}
b_mean_abs_err <- colMeans(b_abs_err) # Take mean over iterations
plot(density(b_mean_abs_err))


# v
v_abs_err <- array(NA, dim = dim(infer_v))
for (i in 1:niter){
  v_abs_err[i,] <- abs(infer_v[i,] - true_v[i])
}
v_mean_abs_err <- colMeans(v_abs_err) # Take mean over iterations
plot(density(v_mean_abs_err))


# t
t_abs_err <- array(NA, dim = dim(infer_t))
for (i in 1:niter){
  t_abs_err[i,] <- abs(infer_t[i,] - true_t[i])
}
t_mean_abs_err <- colMeans(t_abs_err) # Take mean over iterations
plot(density(t_mean_abs_err))


# FA
FA_abs_err <- array(NA, dim = dim(infer_FA))
for (i in 1:niter){
  FA_abs_err[i,] <- abs(infer_FA[i,] - - true_FA[i])
}
FA_mean_abs_err <- colMeans(FA_abs_err) # Take mean over iterations
plot(density(FA_mean_abs_err))




mean_abs_err_df <- data.frame(a_mean_abs_err, b_mean_abs_err, v_mean_abs_err, t_mean_abs_err, FA_mean_abs_err)



mean_abs_err_df %>% ggplot() +
  geom_density(aes(a_mean_abs_err)) +
  theme_minimal()
mean_abs_err_df %>% ggplot() +
  geom_density(aes(b_mean_abs_err)) +
  theme_minimal()
mean_abs_err_df %>% ggplot() +
  geom_density(aes(v_mean_abs_err)) +
  theme_minimal()
mean_abs_err_df %>% ggplot() +
  geom_density(aes(t_mean_abs_err)) +
  theme_minimal()
mean_abs_err_df %>% ggplot() +
  geom_density(aes(FA_mean_abs_err)) +
  theme_minimal()


```




