---
title: "CPT IP param recov"
author: "Andreas"
date: "2025-02-12"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



Load packages
```{r}
library(pacman)
pacman::p_load(tidyverse, cmdstanr, posterior, ggridges, latex2exp, patchwork)

# defining a function for calculating the maximum of the posterior density (not exactly the same as the mode)
MPD <- function(x) {
  density(x)$x[which(density(x)$y==max(density(x)$y))]
}
z <- function(x) {
  return( (x-mean(x))/sd(x) )
}
```


Load data simulation function
```{r}
source("C:/Users/andre/OneDrive - Aarhus universitet/Cognitive Science/Kandidat/Speciale/Analysis/simulation_functions/CPT_IP_w_diff_and_linear_caut_wiener_sim_f.R")
ntrials <- 450
stimuli <- read.csv("CPT_IP_stimuli.csv")
nconditions <- 3
nagents = 1
```


Compile Stan model
```{r}
file <- file.path("C:/Users/andre/OneDrive - Aarhus universitet/Cognitive Science/Kandidat/Speciale/Analysis/Task_specific_models/CPT_IP_diffusion_model_fixed_d.stan")

wiener_CPT_IP_mod = cmdstan_model(file)
```


Simulate a few sessions to inspect prior and posterior

```{r}
# Set parameter values
a <- runif(nagents, 1, 1.7)
b <- runif(nagents, 0.3, 0.7)
v <- runif(nagents, 0.8, 1.7)
t <- runif(nagents, 0.2, 0.25)
d <- c(0.5, 2, 4)
FA <- runif(nagents, -1.5, -0.5)
w <- runif(nagents, 0, 2)

# Simulate data
sim_dat <- data.frame()
for (s in 1:nagents){
  temp_sim <- CPT_IP_w_diff_and_caut_wiener_sim_f(item_type = stimuli$stim_type,
                                                 v[s], a[s], b[s], t[s], d, FA[s], w[s])
  temp_sim$ID = s
  sim_dat <- rbind(sim_dat, temp_sim)
}


# Look at the simulated data

# for (s in 1:nagents){
#   for (c in 1:nconditions){
#     plot(density(sim_dat$RT[sim_dat$button_pressed == 1 &
#                                 sim_dat$correct == 1 &
#                                 sim_dat$condition == c &
#                                 sim_dat$ID == s]), main = paste(paste("RTs (Correct trials). Condition", c), paste("agent", s)))
#     plot(density(sim_dat$RT[sim_dat$button_pressed == 1 &
#                                 sim_dat$correct == 0 &
#                                 sim_dat$condition == c &
#                                 sim_dat$ID == s]), main = paste(paste("RTs (Incorrect trials). Condition", c), paste("agent", s)))
#   }
# }



```



Set priors
```{r}
a_prior_m <- 0
a_prior_sd <- 1
b_prior_m <- 0
b_prior_sd <- 1
v_prior_m <- 0
v_prior_sd <- 1
t_prior_m <- 0
t_prior_sd <- 1
# d_prior_m <- 0
# d_prior_sd <- 1
FA_prior_m <- 0
FA_prior_sd <- 1
w_prior_m <- 0
w_prior_sd <- 1
```


Fit Stan model
```{r}
# Prepare data for Stan
ntrials <- array(NA, dim = nagents)
for (s in 1:nagents){
  ntrials[s] <- length(sim_dat$trial[sim_dat$ID == s]) # number of trials pr participant
}
maxntrials <- max(ntrials) # Maximal number of trials a participant has completed

# Empty arrays to fill
target_present <- array(0, dim = c(maxntrials, nagents))
button_pressed <- array(0, dim = c(maxntrials, nagents))
correct <- array(0, dim = c(maxntrials, nagents))
RT <- array(0, dim = c(maxntrials, nagents))
falsealarm <- array(0, dim = c(maxntrials, nagents))
ncorrectRTs <- array(0, dim = nagents)
nincorrectRTs <- array(0, dim = nagents)
condition_dum <- array(0, dim = c(maxntrials, nconditions, nagents))
min_rt <- array(NA, dim = nagents)

for (s in 1:nagents){
  target_present[1:ntrials[s],s] <- sim_dat$target_present[sim_dat$ID == s]
  button_pressed[1:ntrials[s],s] <- sim_dat$button_pressed[sim_dat$ID == s]
  correct[1:ntrials[s],s] <- sim_dat$correct[sim_dat$ID == s]
  RT[1:ntrials[s],s] <- sim_dat$RT[sim_dat$ID == s]
  falsealarm[1:ntrials[s],s] <- sim_dat$FA_trial[sim_dat$ID == s]
  ncorrectRTs[s] <- sum(sim_dat$button_pressed[sim_dat$correct == 1 &
                                                 sim_dat$RT > 0 &
                                                 sim_dat$ID == s])
  nincorrectRTs[s] <- sum(sim_dat$button_pressed[sim_dat$correct == 0 &
                                                 sim_dat$RT > 0 &
                                                 sim_dat$ID == s])
  min_rt[s] <- min(sim_dat$RT[sim_dat$RT > 0 & sim_dat$ID == s])
  
  for (i in 1:ntrials[s]){
    condition_dum[i, sim_dat$condition[sim_dat$ID == s][i], s] <- 1
  }
}


data <- list(nagents = nagents,
             ntrials = ntrials,
             maxntrials = maxntrials,
             nconditions = nconditions,
             target_present = target_present,
             button_pressed = button_pressed,
             correct = correct,
             RT = RT,
             falsealarm = falsealarm,
             ncorrectRTs = ncorrectRTs,
             nincorrectRTs = nincorrectRTs,
             condition_dum = condition_dum,
             d = d,
             min_rt = min_rt,
             
             a_prior_m = a_prior_m,
             a_prior_sd = a_prior_sd,
             b_prior_m = b_prior_m,
             b_prior_sd = b_prior_sd,
             v_prior_m = v_prior_m,
             v_prior_sd = v_prior_sd,
             t_prior_m = t_prior_m,
             t_prior_sd = t_prior_sd,
             FA_prior_m = FA_prior_m,
             FA_prior_sd = FA_prior_sd,
             # d_prior_m = d_prior_m,
             # d_prior_sd = d_prior_sd,
             w_prior_m = w_prior_m,
             w_prior_sd = w_prior_sd
             )
```

Run model

```{r}
iter_warmup = 1000
iter_sampling = 3000
chains = 3

# Start sampling
samples <- wiener_CPT_IP_mod$sample(
  data = data,
  seed = 123,
  chains = chains,
  parallel_chains = chains,
  iter_warmup = iter_warmup,
  iter_sampling = iter_sampling,
  refresh = 100,
  max_treedepth = 10,
  adapt_delta = 0.99
)

draws_df <- as_draws_df(samples$draws())

#write.csv(draws_df, "CPT_IP_lin_caut_fixed_d_2_agents_draws_18022025.csv")

```


Load single participant draws
```{r}
draws_df <- read.csv("draws_and_true_params/draws_trim_CPT_IP_2025-05-13_102714.267163_agent_1_init0.csv")
true_params <- read.csv("draws_and_true_params/TGM_fixed_d_and_SD_true_params_2025-03-10_125332.675184.csv")

```





Visualize the model fit
```{r}

# Prior Posterior Update checks

### a

p1 <- draws_df %>% ggplot() +
  geom_density(aes(`log_a.1.`), fill = "red", alpha = 0.3) +
  geom_density(aes(log_a_prior), fill = "blue", alpha = 0.3) +
  theme_minimal() +
  labs(title = TeX("PPU check, log(\\textit{a})"),
       x = TeX("log(\\textit{a})"),
       y = TeX("Density")) +
  theme(text = element_text(size = 14, family = "serif"))

p2 <- draws_df %>% ggplot() +
  geom_density(aes(`a.1.`), fill = "red", alpha = 0.3) +
  geom_density(aes(a_prior), fill = "blue", alpha = 0.3) +
  xlim(0,6) +
  geom_vline(xintercept = true_params$a1[1]) +
  theme_minimal() +
  labs(title = TeX("PPU check, \\textit{a}"),
       x = TeX("\\textit{a}"),
       y = TeX("Density")) +
  theme(text = element_text(size = 14, family = "serif"))


### b

p3 <- draws_df %>% ggplot() +
  geom_density(aes(`logit_b.1.`), fill = "red", alpha = 0.3) +
  geom_density(aes(logit_b_prior), fill = "blue", alpha = 0.3) +
  theme_minimal() +
  labs(title = TeX("PPU check, logit(\\textit{b})"),
       x = TeX("logit(\\textit{b})"),
       y = TeX("Density")) +
  theme(text = element_text(size = 14, family = "serif"))

p4 <- draws_df %>% ggplot() +
  geom_density(aes(`b.1.`), fill = "red", alpha = 0.3) +
  geom_density(aes(b_prior), fill = "blue", alpha = 0.3) +
  xlim(0,1) +
  geom_vline(xintercept = true_params$b1[1]) +
  theme_minimal() +
  labs(title = TeX("PPU check, \\textit{b}"),
       x = TeX("\\textit{b}"),
       y = TeX("Density")) +
  theme(text = element_text(size = 14, family = "serif"))


### v

p5 <- draws_df %>% ggplot() +
  geom_density(aes(`log_v.1.`), fill = "red", alpha = 0.3) +
  geom_density(aes(log_v_prior), fill = "blue", alpha = 0.3) +
  theme_minimal() +
  labs(title = TeX("PPU check, log(\\textit{v})"),
       x = TeX("log(\\textit{v})"),
       y = TeX("Density")) +
  theme(text = element_text(size = 14, family = "serif"))

p6 <- draws_df %>% ggplot() +
  geom_density(aes(`v.1.`), fill = "red", alpha = 0.3) +
  geom_density(aes(v_prior), fill = "blue", alpha = 0.3) +
  xlim(0,6) +
  geom_vline(xintercept = true_params$v1[1]) +
  theme_minimal() +
  labs(title = TeX("PPU check, \\textit{v}"),
       x = TeX("\\textit{v}"),
       y = TeX("Density")) +
  theme(text = element_text(size = 14, family = "serif"))


### t

p7 <- draws_df %>% ggplot() +
  geom_density(aes(`cont_t.1.`), fill = "red", alpha = 0.3) +
  geom_density(aes(cont_t_prior), fill = "blue", alpha = 0.3) +
  theme_minimal() +
  labs(title = TeX("PPU check, continuous $\\tau$"),
       x = TeX("Continuous $\\tau$"),
       y = TeX("Density")) +
  theme(text = element_text(size = 14, family = "serif"))

p8 <- draws_df %>% ggplot() +
  geom_density(aes(`t.1.`), fill = "red", alpha = 0.3) +
  geom_density(aes(t_prior.1.), fill = "blue", alpha = 0.3) +
  xlim(0,0.3) +
  geom_vline(xintercept = true_params$t1[1]) +
  theme_minimal() +
  labs(title = TeX("PPU check, $\\tau$"),
       x = TeX("$\\tau$"),
       y = TeX("Density")) +
  theme(text = element_text(size = 14, family = "serif"))


### w

p9 <- draws_df %>% ggplot() +
  geom_density(aes(`log_w.1.`), fill = "red", alpha = 0.3) +
  geom_density(aes(log_w_prior), fill = "blue", alpha = 0.3) +
  theme_minimal() +
  labs(title = TeX("PPU check, log(\\textit{w})"),
       x = TeX("log(\\textit{w})"),
       y = TeX("Density")) +
  theme(text = element_text(size = 14, family = "serif"))

p10 <- draws_df %>% ggplot() +
  geom_density(aes(`w.1.`), fill = "red", alpha = 0.3) +
  geom_density(aes(w_prior), fill = "blue", alpha = 0.3) +
  xlim(0,6) +
  geom_vline(xintercept = true_params$w[1]) +
  theme_minimal() +
  labs(title = TeX("PPU check, \\textit{w}"),
       x = TeX("\\textit{w}"),
       y = TeX("Density")) +
  theme(text = element_text(size = 14, family = "serif"))



### FA

p11 <- draws_df %>% ggplot() +
  geom_density(aes(`log_FA.1.`), fill = "red", alpha = 0.3) +
  geom_density(aes(log_FA_prior), fill = "blue", alpha = 0.3) +
  theme_minimal() +
  labs(title = TeX("PPU check, log(\\textit{FA})"),
       x = TeX("log(\\textit{FA})"),
       y = TeX("Density")) +
  theme(text = element_text(size = 14, family = "serif"))

p12 <- draws_df %>% ggplot() +
  geom_density(aes(`FA.1.`), fill = "red", alpha = 0.3) +
  geom_density(aes(FA_prior), fill = "blue", alpha = 0.3) +
  xlim(0,6) +
  geom_vline(xintercept = - true_params$FA1[1]) +
  theme_minimal() +
  labs(title = TeX("PPU check, \\textit{FA}"),
       x = TeX("\\textit{FA}"),
       y = TeX("Density")) +
  theme(text = element_text(size = 14, family = "serif"))


(p1 + p3 + p5 + p7 + p9 + p11) / (p2 + p4 + p6 + p8 + p10 + p12)


```


Chain checks

```{r}
ccp1 <- draws_df %>% ggplot() +
  geom_line(aes(x = .iteration, y = log_a.1., color = as.factor(.chain))) +
  theme(legend.position = "none")

ccp2 <- draws_df %>% ggplot() +
  geom_line(aes(x = .iteration, y = log_v.1., color = as.factor(.chain))) +
  theme(legend.position = "none")

ccp3 <- draws_df %>% ggplot() +
  geom_line(aes(x = .iteration, y = logit_b.1., color = as.factor(.chain))) +
  theme(legend.position = "none")

ccp4 <- draws_df %>% ggplot() +
  geom_line(aes(x = .iteration, y = cont_t.1., color = as.factor(.chain))) +
  theme(legend.position = "none")

ccp5 <- draws_df %>% ggplot() +
  geom_line(aes(x = .iteration, y = log_w.1., color = as.factor(.chain)))

(ccp1 + ccp2 + ccp3) / (ccp4 + ccp5)
```




PP checks

```{r}
source("C:/Users/andre/OneDrive - Aarhus universitet/Cognitive Science/Kandidat/Speciale/Analysis/visualization_functions/wiener_ppcheck_v2.R")
```


Load Simulated data
```{r}
sim_dat <- read.csv("TGM_fixed_d_and_SD_sim_dat_2025-03-10_125332.675184.csv")

d_vec <- c(0.5, 2, 4)
```

```{r}
correct_RTs <- sim_dat$RT[sim_dat$correct == 1 & sim_dat$button_pressed == 1 & sim_dat$ID == 1]
ntrials_pr_condition <- c(150,150,150)
nconditions <- 3

wiener_ppcheck(RT_data = correct_RTs,
               ntrials_pr_condition = ntrials_pr_condition, 
               a_samples = draws_df$a.1.[draws_df$ID == 1],
               b_samples = draws_df$b.1.[draws_df$ID == 1],
               v_samples = draws_df$v.1.[draws_df$ID == 1],
               t_samples = draws_df$t.1.[draws_df$ID == 1],
               w_samples = draws_df$w.1.[draws_df$ID == 1],
               nconditions = nconditions,
               d = d_vec
               )

wiener_ppcheck(RT_data = correct_RTs,
               ntrials_pr_condition = ntrials_pr_condition, 
               a_samples = draws_df$a_prior[draws_df$ID == 1],
               b_samples = draws_df$b_prior[draws_df$ID == 1],
               v_samples = draws_df$v_prior[draws_df$ID == 1],
               t_samples = draws_df$t_prior.1.[draws_df$ID == 1],
               w_samples = draws_df$w_prior[draws_df$ID == 1],
               nconditions = nconditions,
               d = d_vec, 
               prior_only = TRUE
               )
```


PP checks of hit rate and com. rate

```{r}
theta <- function(a, b, v, w, d, FA, target_present) {
  if (target_present == 1){
    bias <- b
  } else {
    bias <- rep(1, length(b)) - b
  }
  EEA_given_d <- v - (0.2 * d)
  EEA_given_d <- ifelse(EEA_given_d < 0, 0, EEA_given_d)
  EEA <- EEA_given_d - FA
  caut <- a + (0.2 * w * d)
  
  thet <- 1-( (1 - exp(-2*EEA*caut*(1-bias))) / (exp(2*EEA*caut*bias) - exp(-2*EEA*caut*(1-bias))) )
  thet <- ifelse(is.nan(thet), bias, thet)
  return(thet)
}
```


Hit Rate
```{r}
# Prior hitrate

n_conditions <- 3
theta_prior <- array(NA, dim = c(12000, 3))

for (c in 1:3) {
  for (i in 1:12000){}
    theta_prior[,c] <- theta(draws_df$a_prior,
                                draws_df$b_prior,
                                draws_df$v_prior,
                                draws_df$w_prior,
                                d = d_vec[c],
                                FA = 0,
                                target_present = 1)
}

hit_rate_prior_df <- data.frame(theta_prior)

colnames(hit_rate_prior_df) <- c("CPT-IP cond. 1", "CPT-IP cond. 2", "CPT-IP cond. 3")

hit_rate_prior_df <- hit_rate_prior_df %>% pivot_longer(names_to = "Condition", cols = everything())

cond_order <- c("CPT-IP cond. 1", "CPT-IP cond. 2", "CPT-IP cond. 3")

hit_rate_prior_df <- hit_rate_prior_df %>% 
  mutate(Condition = factor(Condition, levels = cond_order)) %>% 
  arrange(Condition)


hit_rate_prior_df %>% 
  ggplot() +
  geom_density(aes(value, color = Condition)) +
  theme_minimal() +
  labs(title = "Prior Hit Rate predictions",
       x = "Hit Rate",
       y = "Density") +
  theme(text = element_text(size = 14, family = "serif"))
```


```{r}
# Posterior hit rate

theta_post <- array(NA, dim = c(12000, 3))

for (c in 1:3) {
  for (i in 1:12000){}
    theta_post[,c] <- theta(draws_df$a.1.,
                                draws_df$b.1.,
                                draws_df$v.1.,
                                draws_df$w.1.,
                                d = d_vec[c],
                                FA = 0,
                                target_present = 1)
}

hit_rate_post_df <- data.frame(theta_post)

colnames(hit_rate_post_df) <- c("CPT-IP cond. 1", "CPT-IP cond. 2", "CPT-IP cond. 3")

hit_rate_post_df <- hit_rate_post_df %>% pivot_longer(names_to = "Condition", cols = everything())

cond_order <- c("CPT-IP cond. 1", "CPT-IP cond. 2", "CPT-IP cond. 3")


hit_rate_post_df <- hit_rate_post_df %>% 
  mutate(Condition = factor(Condition, levels = cond_order)) %>% 
  arrange(Condition)

hit_rate_post_df$cond_num <- as.numeric(str_sub(hit_rate_post_df$Condition, -1, -1))

true_hitrate <- data.frame("cond_num" = c(1,2,3), "true_hitrate" = NA)
for (c in 1:n_conditions){
  true_hitrate$true_hitrate[c] <- sum(sim_dat$button_pressed[sim_dat$target_present == 1 &
                                                  sim_dat$ID == 1 &
                                                  sim_dat$condition == c]) / 30
}
true_hitrate$true_hitrate[2] <- true_hitrate$true_hitrate[2] + 0.003

hit_rate_post_df <- merge(hit_rate_post_df, true_hitrate, by = "cond_num")

hit_rate_post_df %>% 
  ggplot() +
  geom_density(aes(value, color = Condition)) +
  geom_vline(aes(xintercept = true_hitrate, color = Condition)) +
  theme_minimal() +
  labs(title = "Posterior Hit Rate predictions",
       x = "Hit Rate",
       y = "Density") +
  guides(color = guide_legend(title = "Condition")) +
  theme(text = element_text(size = 14, family = "serif"))

```


Com. Rate
```{r}
# Prior comrate

n_conditions <- 3
theta_prior <- array(NA, dim = c(12000, 3))

for (c in 1:3) {
  for (i in 1:12000){}
    theta_prior[,c] <- 1-theta(draws_df$a_prior,
                                draws_df$b_prior,
                                draws_df$v_prior,
                                draws_df$w_prior,
                                d = d_vec[c],
                                FA = 0,
                                target_present = 1)
}

com_rate_prior_df <- data.frame(theta_prior)

colnames(com_rate_prior_df) <- c("CPT-IP cond. 1", "CPT-IP cond. 2", "CPT-IP cond. 3")

com_rate_prior_df <- com_rate_prior_df %>% pivot_longer(names_to = "Condition", cols = everything())

cond_order <- c("CPT-IP cond. 1", "CPT-IP cond. 2", "CPT-IP cond. 3")

com_rate_prior_df <- com_rate_prior_df %>% 
  mutate(Condition = factor(Condition, levels = cond_order)) %>% 
  arrange(Condition)


com_rate_prior_df %>% 
  ggplot() +
  geom_density(aes(value, color = Condition)) +
  theme_minimal() +
  labs(title = "Prior Com. Rate predictions",
       x = "Hit Rate",
       y = "Density") +
  theme(text = element_text(size = 14, family = "serif"))
```


```{r}
# Posterior com rate

theta_post <- array(NA, dim = c(12000, 3))

for (c in 1:3) {
  for (i in 1:12000){}
    theta_post[,c] <- 1 - theta(draws_df$a.1.,
                                draws_df$b.1.,
                                draws_df$v.1.,
                                draws_df$w.1.,
                                d = d_vec[c],
                                FA = 0,
                                target_present = 1)
}

com_rate_post_df <- data.frame(theta_post)

colnames(com_rate_post_df) <- c("CPT-IP cond. 1", "CPT-IP cond. 2", "CPT-IP cond. 3")

com_rate_post_df <- com_rate_post_df %>% pivot_longer(names_to = "Condition", cols = everything())

cond_order <- c("CPT-IP cond. 1", "CPT-IP cond. 2", "CPT-IP cond. 3")

com_rate_post_df <- com_rate_post_df %>% 
  mutate(Condition = factor(Condition, levels = cond_order)) %>% 
  arrange(Condition)

com_rate_post_df$cond_num <- as.numeric(str_sub(com_rate_post_df$Condition, -1, -1))

true_comrate <- data.frame("cond_num" = c(1,2,3), "true_comrate" = NA)
for (c in 1:n_conditions){
  true_comrate$true_comrate[c] <- sum(sim_dat$button_pressed[sim_dat$target_present == 0 &
                                                  sim_dat$ID == 1 &
                                                  sim_dat$condition == c]) / 120
}
#true_comrate$true_comrate[2] <- true_comrate$true_comrate[2] + 0.003

com_rate_post_df <- merge(com_rate_post_df, true_comrate, by = "cond_num")


com_rate_post_df %>% 
  ggplot() +
  geom_density(aes(value, color = Condition)) +
  geom_vline(aes(xintercept = true_comrate, color = Condition)) +
  theme_minimal() +
  labs(title = "Posterior Com. Rate predictions",
       x = "Com. Rate",
       y = "Density") +
  guides(color = guide_legend(title = "Condition")) +
  theme(text = element_text(size = 14, family = "serif"))

```




```{r}
"""
# Hit rate
n_target_trials <- 90
# Prior

theta_prior <- array(NA, dim = c(12000, nconditions))
theta_prior[, 1] <- draws_df$Hit_Rate_prior.3.
theta_prior[, 2] <- draws_df$Hit_Rate_prior.153.
theta_prior[, 3] <- draws_df$Hit_Rate_prior.303.

n_hits_prior <- array(NA, dim = 3000)
sample_idx <- floor(runif(3000, min = 1, max = nrow(draws_df)))

for (i in 1:length(sample_idx)){
  idx <- sample_idx[i]
  temp <- 0
  
  for (c in 1:nconditions){
    temp <- temp + rbinom(1, n_target_trials/3, theta_prior[idx,c])
  }
  n_hits_prior[i] <- temp
}






# Posterior
theta <- array(NA, dim = c(12000, nconditions))
theta[, 1] <- draws_df$theta.3.1.
theta[, 2] <- draws_df$theta.153.1.
theta[, 3] <- draws_df$theta.303.1.


n_hits_post <- array(NA, dim = 3000)
sample_idx <- floor(runif(3000, min = 1, max = nrow(draws_df)))

for (i in 1:length(sample_idx)){
  idx <- sample_idx[i]
  temp <- 0
  
  for (c in 1:nconditions){
    temp <- temp + rbinom(1, n_target_trials/3, theta_random[idx,c])
  }
  n_hits_post[i] <- temp
}

hits <- data.frame(n_hits_prior = n_hits_prior, n_hits_post = n_hits_post)
hits <- hits %>% mutate(
  hitrate_prior = n_hits_prior / 90,
  hitrate_post = n_hits_post / 90
)

hits %>% ggplot() +
  geom_density(aes(x = hitrate_prior), fill = "blue", alpha = 0.3) +
  theme_minimal() +
  labs(title = TeX("Prior Hit Rate prediction"),
       x = TeX("Hit Rate"),
       y = TeX("Density")) +
  theme(text = element_text(size = 14, family = "serif"))


true_hitrate <- sum(sim_dat$button_pressed[sim_dat$ID == 1 & sim_dat$target_present == 1 & sim_dat$task_name == "CPT-IP"]) / n_target_trials

hits %>% ggplot() +
  geom_density(aes(x = hitrate_post), fill = "red", alpha = 0.3) +
  theme_minimal() +
  geom_vline(xintercept = true_hitrate) +
  labs(title = TeX("Posterior Hit Rate prediction"),
       x = TeX("Hit Rate"),
       y = TeX("Density")) +
  theme(text = element_text(size = 14, family = "serif"))


### Com. rate is seen on theta for distractor trials
### varies between FA trials and random trials, so we do both

# random trial : 1, 151, 301
# FA trial : 5, 295, 305
n_FA_trials <- sum(sim_dat$FA_trial[sim_dat$task_name == "CPT-IP" & sim_dat$ID == 1])
n_ran_trials <- 450 - sum(sim_dat$target_present[sim_dat$task_name == "CPT-IP" & sim_dat$ID == 1]) - n_FA_trials


# generate predictions of commisions

# Prior

theta_random_prior <- array(NA, dim = c(12000, nconditions))
theta_random_prior[, 1] <- draws_df$Hit_Rate_prior.1.
theta_random_prior[, 2] <- draws_df$Hit_Rate_prior.151.
theta_random_prior[, 3] <- draws_df$Hit_Rate_prior.301.

theta_FA_prior <- array(NA, dim = c(12000, nconditions))
theta_FA_prior[, 1] <- draws_df$Hit_Rate_prior.5.
theta_FA_prior[, 2] <- draws_df$Hit_Rate_prior.295.
theta_FA_prior[, 3] <- draws_df$Hit_Rate_prior.305.

n_coms_prior <- array(NA, dim = 3000)
sample_idx <- floor(runif(3000, min = 1, max = nrow(draws_df)))

for (i in 1:length(sample_idx)){
  idx <- sample_idx[i]
  temp <- 0
  
  for (c in 1:nconditions){
    temp <- temp + rbinom(1, n_ran_trials/3, 1-theta_random_prior[idx,c])
    temp <- temp + rbinom(1, n_FA_trials/3, 1-theta_FA_prior[idx,c])
  }
  n_coms_prior[i] <- temp
}



# Posterior
theta_random <- array(NA, dim = c(12000, nconditions))
theta_random[, 1] <- draws_df$theta.1.1.
theta_random[, 2] <- draws_df$theta.151.1.
theta_random[, 3] <- draws_df$theta.301.1.

theta_FA <- array(NA, dim = c(12000, nconditions))
theta_FA[, 1] <- draws_df$theta.5.1.
theta_FA[, 2] <- draws_df$theta.295.1.
theta_FA[, 3] <- draws_df$theta.305.1.

n_coms_post <- array(NA, dim = 3000)
sample_idx <- floor(runif(3000, min = 1, max = nrow(draws_df)))

for (i in 1:length(sample_idx)){
  idx <- sample_idx[i]
  temp <- 0
  
  for (c in 1:nconditions){
    temp <- temp + rbinom(1, n_ran_trials/3, 1-theta_random[idx,c])
    temp <- temp + rbinom(1, n_FA_trials/3, 1-theta_FA[idx,c])
  }
  n_coms_post[i] <- temp
}

coms <- data.frame(n_coms_prior = n_coms_prior, n_coms_post = n_coms_post)
coms <- coms %>% mutate(
  comrate_prior = n_coms_prior / 360,
  comrate_post = n_coms_post / 360
)

coms %>% ggplot() +
  geom_density(aes(x = comrate_prior), fill = "blue", alpha = 0.3) +
  theme_minimal() +
  labs(title = TeX("Prior Com. Rate prediction"),
       x = TeX("Com. Rate"),
       y = TeX("Density")) +
  theme(text = element_text(size = 14, family = "serif"))

true_comrate <- sum(sim_dat$button_pressed[sim_dat$ID == 1 & sim_dat$target_present == 0 & sim_dat$task_name == "CPT-IP"]) / (n_ran_trials + n_FA_trials)

coms %>% ggplot() +
  geom_density(aes(x = comrate_post), fill = "red", alpha = 0.3) +
  theme_minimal() +
  geom_vline(xintercept = true_comrate) +
  labs(title = TeX("Posterior Com. Rate prediction"),
       x = TeX("Com. Rate"),
       y = TeX("Density")) +
  theme(text = element_text(size = 14, family = "serif"))
"""
```






Load recovery data with 30 agents and fixed d, now linear caut
```{r}
filenames <- list.files(path = "C:/Users/andre/OneDrive - Aarhus universitet/Cognitive Science/Kandidat/Speciale/Analysis/Task_specific_models/draws_and_true_params", pattern = "draws_trim_CPT_IP_2025-05-12_092117.7064_agent_\\d+_init0.csv")

draws_df <- data.frame()

for (filename in filenames) {
  single_agent_draws <- read.csv(paste0("draws_and_true_params/", filename))
  draws_df <- rbind(draws_df, single_agent_draws)
}


```

```{r}
draws_df <- draws_df %>% dplyr::select(-X)
true_params <- true_params %>% dplyr::select(-X) %>% 
  dplyr::select(s, a1, b1, v1, t1, w, FA1)

colnames(draws_df) <- c("a", "b", "v", "t", "FA", "w", "ID")

colnames(true_params) <- c("ID", "true_a", "true_b","true_v", "true_t", "true_w", "true_FA")

recov_summa <- draws_df %>% group_by(ID) %>% summarize(a = mean(a),
                                                      b = mean(b),
                                                      v = mean(v),
                                                      t = mean(t),
                                                      FA = mean(FA),
                                                      w = mean(w))
recov_summa <- merge(recov_summa, true_params, by = "ID")

```


Visualize recovery

```{r}
library(latex2exp)

recplt_a <- recov_summa %>% ggplot() +
  geom_point(aes(x = true_a, y = a)) +
  geom_abline(slope = 1, intercept = 0, color = "red") +
  theme_minimal() +
  labs(title = expression(paste("Recovery of parameter ", italic("a"))),
       x = expression(paste("True ", italic("a"))),
       y = expression(paste("Mean inferred ", italic("a")))) +
  theme(text = element_text(size = 14, family = "serif"))

recplt_b <- recov_summa %>% ggplot() +
  geom_point(aes(x = true_b, y = b)) +
  geom_abline(slope = 1, intercept = 0, color = "red") +
  theme_minimal() +
  labs(title = expression(paste("Recovery of parameter ", italic("b"))),
       x = expression(paste("True ", italic("b"))),
       y = expression(paste("Mean inferred ", italic("b")))) +
  theme(text = element_text(size = 14, family = "serif"))

recplt_v <- recov_summa %>% ggplot() +
  geom_point(aes(x = true_v, y = v)) +
  geom_abline(slope = 1, intercept = 0, color = "red") +
  theme_minimal() +
  labs(title = expression(paste("Recovery of parameter ", italic("v"))),
       x = expression(paste("True ", italic("v"))),
       y = expression(paste("Mean inferred ", italic("v")))) +
  theme(text = element_text(size = 14, family = "serif"))

recplt_t <- recov_summa %>% ggplot() +
  geom_point(aes(x = true_t, y = t)) +
  geom_abline(slope = 1, intercept = 0, color = "red") +
  theme_minimal() +
  labs(title = TeX("Recovery of parameter $\\tau$"),
       x = TeX("True $\\tau$"),
       y = TeX("Mean inferred $\\tau$")) +
  theme(text = element_text(size = 14, family = "serif"))

recplt_w <- recov_summa %>% ggplot() +
  geom_point(aes(x = true_w, y = w)) +
  geom_abline(slope = 1, intercept = 0, color = "red") +
  theme_minimal() +
  labs(title = expression(paste("Recovery of parameter ", italic("w"))),
       x = expression(paste("True ", italic("w"))),
       y = expression(paste("Mean inferred ", italic("w")))) +
  theme(text = element_text(size = 14, family = "serif"))

recplt_FA <- recov_summa %>% ggplot() +
  geom_point(aes(x = true_FA, y = -FA)) +
  geom_abline(slope = 1, intercept = 0, color = "red") +
  theme_minimal() +
  labs(title = expression(paste("Recovery of parameter ", italic("FA"))),
       x = expression(paste("True ", italic("FA"))),
       y = expression(paste("Mean inferred ", italic("FA")))) +
  theme(text = element_text(size = 14, family = "serif"))

(recplt_a + recplt_b + recplt_v) / (recplt_t + recplt_w + recplt_FA)
```










Fit ordinal regression
```{r}
library(ordinal)
# Get ranking of the true parameters
true_params$rank_a <- rank(true_params$true_a)
true_params$rank_b <- rank(true_params$true_b)
true_params$rank_v <- rank(true_params$true_v)
true_params$rank_t <- rank(true_params$true_t)
true_params$rank_w <- rank(true_params$true_w)
true_params$rank_FA <- rank(true_params$true_FA)
ranking_d <- true_params %>% dplyr::select(ID, starts_with("rank"))


draws_df <- merge(draws_df, ranking_d, by = "ID") # merge rankings with the draws

draws_df$FA <- - draws_df$FA # Flip sign of the FA effect

draws_df$rank_a <- as.factor(draws_df$rank_a)
draws_df$rank_b <- as.factor(draws_df$rank_b)
draws_df$rank_v <- as.factor(draws_df$rank_v)
draws_df$rank_t <- as.factor(draws_df$rank_t)
draws_df$rank_w <- as.factor(draws_df$rank_w)
draws_df$rank_FA <- as.factor(draws_df$rank_FA)

# Get z-scores
draws_df <- draws_df %>% 
  mutate(
    a_z = z(a),
    b_z = z(b),
    v_z = z(v),
    t_z = z(t),
    w_z = z(w),
    FA_z = z(FA)
  )


# Fit models for each param

m_a <- clm(rank_a ~ a_z, data = draws_df)
m_b <- clm(rank_b ~ b_z, data = draws_df)
m_v <- clm(rank_v ~ v_z, data = draws_df)
m_t <- clm(rank_t ~ t_z, data = draws_df)
m_w <- clm(rank_w ~ w_z, data = draws_df)
m_FA <- clm(rank_FA ~ FA_z, data = draws_df)


m_a$coefficients["a_z"]
m_b$coefficients["b_z"]
m_v$coefficients["v_z"]
m_t$coefficients["t_z"]
m_w$coefficients["w_z"]
# m_FA$coefficients["FA_z"]


summary(m_a)
summary(m_b)
summary(m_v)
summary(m_t)
summary(m_w)
# summary(m_FA)
```






Get distribution of mean absolute error error for each param.

Mean of absolute errors

```{r}
nagents <- 30
niter <- 12000



# a
infer_a <- array(draws_df$a, dim = c(niter, nagents))
infer_a <- t(infer_a) # transpose so that we have a row for each agent and column for each sample
a_abs_err <- array(NA, dim = dim(infer_a))
for (i in 1:nagents){
  a_abs_err[i,] <- abs(infer_a[i,] - true_params$true_a[i])
}
a_mean_abs_err <- colMeans(a_abs_err)
plot(density(a_mean_abs_err))


# b
infer_b <- array(draws_df$b, dim = c(niter, nagents))
infer_b <- t(infer_b) # transpose so that we have a row for each agent and column for each sample
b_abs_err <- array(NA, dim = dim(infer_b))
for (i in 1:nagents){
  b_abs_err[i,] <- abs(infer_b[i,] - true_params$true_b[i])
}
b_mean_abs_err <- colMeans(b_abs_err)
plot(density(b_mean_abs_err))



# v
infer_v <- array(draws_df$v, dim = c(niter, nagents))
infer_v <- t(infer_v) # transpose so that we have a row for each agent and column for each sample
v_abs_err <- array(NA, dim = dim(infer_v))
for (i in 1:nagents){
  v_abs_err[i,] <- abs(infer_v[i,] - true_params$true_v[i])
}
v_mean_abs_err <- colMeans(v_abs_err)
plot(density(v_mean_abs_err))


# t
infer_t <- array(draws_df$t, dim = c(niter, nagents))
infer_t <- t(infer_t) # transpose so that we have a row for each agent and column for each sample
t_abs_err <- array(NA, dim = dim(infer_t))
for (i in 1:nagents){
  t_abs_err[i,] <- abs(infer_t[i,] - true_params$true_t[i])
}
t_mean_abs_err <- colMeans(t_abs_err)
plot(density(t_mean_abs_err))


# w
infer_w <- array(draws_df$w, dim = c(niter, nagents))
infer_w <- t(infer_w) # transpose so that we have a row for each agent and column for each sample
w_abs_err <- array(NA, dim = dim(infer_w))
for (i in 1:nagents){
  w_abs_err[i,] <- abs(infer_w[i,] - true_params$true_w[i])
}
w_mean_abs_err <- colMeans(w_abs_err)
plot(density(w_mean_abs_err))


# FA
infer_FA <- array(draws_df$FA, dim = c(niter, nagents))
infer_FA <- t(infer_FA) # transpose so that we have a row for each agent and column for each sample
FA_abs_err <- array(NA, dim = dim(infer_FA))
for (i in 1:nagents){
  FA_abs_err[i,] <- abs(infer_FA[i,] - true_params$true_FA[i])
}
FA_mean_abs_err <- colMeans(FA_abs_err)
plot(density(FA_mean_abs_err))




mean_abs_err_df <- data.frame(a_mean_abs_err, b_mean_abs_err, v_mean_abs_err, t_mean_abs_err, w_mean_abs_err, FA_mean_abs_err)



mean_abs_err_df %>% ggplot() +
  geom_density(aes(a_mean_abs_err)) +
  theme_minimal()
mean_abs_err_df %>% ggplot() +
  geom_density(aes(b_mean_abs_err)) +
  theme_minimal()
mean_abs_err_df %>% ggplot() +
  geom_density(aes(v_mean_abs_err)) +
  theme_minimal()
mean_abs_err_df %>% ggplot() +
  geom_density(aes(t_mean_abs_err)) +
  theme_minimal()
mean_abs_err_df %>% ggplot() +
  geom_density(aes(w_mean_abs_err)) +
  theme_minimal()
mean_abs_err_df %>% ggplot() +
  geom_density(aes(FA_mean_abs_err)) +
  theme_minimal()
```




Check correlations

```{r}
recov_summa <- recov_summa %>%
  mutate(a_error = a - true_a,
         b_error = b - true_b,
         v_error = v - true_v,
         t_error = t - true_t,
         w_error = w - true_w)
```

```{r}
recov_summa %>% ggplot() +
  geom_point(aes(a_error, w_error))
cor(recov_summa$a_error, recov_summa$w_error)

recov_summa %>% ggplot() +
  geom_point(aes(a, w))

recov_summa %>% ggplot() +
  geom_point(aes(a_error, v_error))
```




