---
title: "TGM validation"
author: "Andreas"
date: "2025-01-16"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



Load packages
```{r}
library(pacman)
pacman::p_load(tidyverse, cmdstanr, posterior, ggridges, MASS)

z <- function(x) {
  return( (x-mean(x))/sd(x) )
}

```


Load data simulation functions
```{r}
# For CPT-IP
source("C:/Users/andre/OneDrive - Aarhus universitet/Cognitive Science/Kandidat/Speciale/Analysis/simulation_functions/CPT_IP_w_diff_and_linear_caut_wiener_sim_f.R")
# For Conners' CPT
source("C:/Users/andre/OneDrive - Aarhus universitet/Cognitive Science/Kandidat/Speciale/Analysis/simulation_functions/Conners_TGM_sim_f.R")
# For RVP
source("C:/Users/andre/OneDrive - Aarhus universitet/Cognitive Science/Kandidat/Speciale/Analysis/simulation_functions/RVP_TGM_sim_f.R")
```


Simulation environment
```{r}
nagents <- 30
ntrials_pr_task <- c(450, 360, 300) # CPT-IP, Conners', RVP
nconditions_pr_task <- c(3, 1, 1)
ntargets_pr_task <- c(90, 324, 24)
nFAtrials_RVP <- 5
CPT_IP_stimuli <- read.csv("CPT_IP_stimuli.csv")
ntasks <- 3
```


Simulate data

--Set true param values
```{r}
# Set true param values
a_m <- runif(nagents, 1, 2)
a_sd <- runif(nagents, 0.01, 0.03)
b_m <- runif(nagents, 0.3, 0.7)
b_sd <- runif(nagents,  0.01, 0.03)
v_m <- runif(nagents, 1, 2)
v_sd <- runif(nagents, 0.01, 0.03)
t_m <- runif(nagents, 0.2, 0.25)
t_sd <- runif(nagents, 0.002, 0.004)

FA_means <- c(0, 0, 0)
corr_matrix <- matrix(c(1, 0.9, 0.9,
              0.9, 1, 0.9,
              0.9, 0.9, 1), nrow = 3)
variances <- diag(1, nrow = 3, ncol = 3) # In this case, Identity matrix
covar_matrix <- variances %*% corr_matrix %*% variances



FA <- mvrnorm(nagents, mu = FA_means, Sigma = corr_matrix) # Generate 3 correlated variables with m=0 and sd=1
FA[,1] <- FA[,1] * 0.2 - 1.2 # change the mean and sd of each variable, so we dont get positive values of FA
FA[,2] <- FA[,2] * 0.2 - 1.5
FA[,3] <- FA[,3] * 0.2 - 0.6

w <- runif(nagents, 0, 2)

d <- array(c(0.5,2,4,
             0.1,NA,NA,
             1,NA,NA), dim = c(ntasks, max(nconditions_pr_task)))
d_vec <- array(d, dim = 9)
d_vec <- d_vec[!is.na(d_vec)]
```

-- Generate data
```{r}
# Task level param values
true_as <- array(NA, dim = c(nagents, ntasks))
true_bs <- array(NA, dim = c(nagents, ntasks))
true_vs <- array(NA, dim = c(nagents, ntasks))
true_ts <- array(NA, dim = c(nagents, ntasks))

sim_dat <- data.frame()

for (s in 1:nagents){
  # draw param values for each of the tasks
  true_as[s,] <- rnorm(ntasks, a_m[s], a_sd[s])
  true_bs[s,] <- rnorm(ntasks, b_m[s], b_sd[s])
  true_vs[s,] <- rnorm(ntasks, v_m[s], v_sd[s])
  true_ts[s,] <- rnorm(ntasks, t_m[s], t_sd[s])
  
  # Generate CPT-IP data
  CPT_IP_sim <- CPT_IP_w_diff_and_caut_wiener_sim_f(item_type = CPT_IP_stimuli$stim_type,
                                                    v = true_vs[s,1], a = true_as[s,1],
                                                    b = true_bs[s,1], tau = true_ts[s,1],
                                                    d = d[,1], FA = FA[s,1], w = w[s])

  CPT_IP_sim <- CPT_IP_sim %>% subset(select = -item_type)
  CPT_IP_sim$ID <- s
  CPT_IP_sim$task_name <- "CPT-IP"
  CPT_IP_sim$task_num <- 1
  sim_dat <- rbind(sim_dat, CPT_IP_sim)
  
  # Generate Conners' CPT data
  conners_sim <- Conners_TGM_sim_f(ntrials_pr_task[2], ntargets_pr_task[2],
                                   true_vs[s,2], true_as[s,2],
                                   true_bs[s,2], true_ts[s,2],
                                   d[1,2], FA[s,2], w[s])
  conners_sim$ID <- s
  conners_sim$task_name <- "Conners"
  conners_sim$task_num <- 2
  conners_sim$condition <- 4
  sim_dat <- rbind(sim_dat, conners_sim)
  
  # Generate RVP data
  RVP_sim <- RVP_TGM_sim_f(ntrials_pr_task[3], ntargets_pr_task[3], nFAtrials_RVP,
                           true_vs[s,3], true_as[s,3],
                           true_bs[s,3], true_ts[s,3],
                           d[1,3], FA[s,3], w[s])
  RVP_sim$RT <- ifelse(RVP_sim$correct == 1, RVP_sim$RT, 0) # No incorrect RTs in RVP
  RVP_sim$ID <- s
  RVP_sim$task_name <- "RVP"
  RVP_sim$task_num <- 3
  RVP_sim$condition <- 5
  sim_dat <- rbind(sim_dat, RVP_sim)
  
}
sim_dat$incorrectRTs_present <- ifelse(sim_dat$task_name == "RVP", 0, 1)

```


Save true param values to csv
```{r}
true_params <- data.frame(s = seq(1:nagents), a_m, a_sd, b_m, b_sd, v_m, v_sd, t_m, t_sd, w)

for (task in 1:ntasks){
  tnum <- as.character(task)
  temp <- data.frame(matrix(NA, nrow = nagents, ncol = 5))
  colnames(temp) <- c(paste0("a", tnum),
                      paste0("b", tnum),
                      paste0("v", tnum),
                      paste0("t", tnum),
                      paste0("FA", tnum))
  temp[,1] <- true_as[,task]
  temp[,2] <- true_bs[,task]
  temp[,3] <- true_vs[,task]
  temp[,4] <- true_ts[,task]
  temp[,5] <- FA[,task]
  true_params <- cbind(true_params, temp)
}

datetime <- as.character(Sys.time())
datetime <- gsub(":", "", datetime)

write.csv(true_params, paste("TGM_true_params", paste0(datetime, ".csv")))

```





Compile Stan model
```{r}
file <- file.path("C:/Users/andre/OneDrive - Aarhus universitet/Cognitive Science/Kandidat/Speciale/Analysis/Task_general_model/task_general_diffusion_mod.stan")

TGM_mod <- cmdstan_model(file)
```


Fit Stan model

-- Set Priors
```{r}
a_M_prior_m <- 0
a_M_prior_sd <- 1
a_SD_prior_m <- 0
a_SD_prior_sd <- 0.3
b_M_prior_m <- 0
b_M_prior_sd <- 1
b_SD_prior_m <- 0
b_SD_prior_sd <- 0.3
v_M_prior_m <- 0
v_M_prior_sd <- 1
v_SD_prior_m <- 0
v_SD_prior_sd <- 0.3
t_M_prior_m <- 0
t_M_prior_sd <- 1
t_SD_prior_m <- 0
t_SD_prior_sd <- 0.2

d_prior_m <- 0
d_prior_sd <- 1
w_prior_m <- 0
w_prior_sd <- 1
FA_prior_m <- 0
```



-- Prepare data for Stan
```{r}
ntrials <- array(NA, dim = nagents)
for (s in 1:nagents){
  ntrials[s] <- length(sim_dat$trial[sim_dat$ID == s]) # number of trials pr participant
}

maxntrials <- max(ntrials) # Maximal number of trials a participant has completed
nconditions <- sum(nconditions_pr_task) # Total number of conditions

# Empty arrays to fill
target_present <- array(0, dim = c(maxntrials, nagents))
button_pressed <- array(0, dim = c(maxntrials, nagents))
correct <- array(0, dim = c(maxntrials, nagents))
RT <- array(0, dim = c(maxntrials, nagents))
falsealarm <- array(0, dim = c(maxntrials, nagents))
incorrectRTs_present <- array(0, dim = c(maxntrials, nagents))
ncorrectRTs <- array(0, dim = nagents)
nincorrectRTs <- array(0, dim = nagents)
condition_dum <- array(0, dim = c(maxntrials, nconditions, nagents))
task_dum <- array(0, dim = c(maxntrials, ntasks, nagents))
min_rt <- array(0, dim = c(nagents, ntasks))



for (s in 1:nagents){
  target_present[1:ntrials[s],s] <- sim_dat$target_present[sim_dat$ID == s]
  button_pressed[1:ntrials[s],s] <- sim_dat$button_pressed[sim_dat$ID == s]
  correct[1:ntrials[s],s] <- sim_dat$correct[sim_dat$ID == s]
  RT[1:ntrials[s],s] <- sim_dat$RT[sim_dat$ID == s]
  falsealarm[1:ntrials[s],s] <- sim_dat$FA_trial[sim_dat$ID == s]
  incorrectRTs_present[1:ntrials[s],s] <- sim_dat$incorrectRTs_present[sim_dat$ID == s]
  ncorrectRTs[s] <- sum(sim_dat$button_pressed[sim_dat$correct == 1 &
                                                 sim_dat$RT > 0 &
                                                 sim_dat$ID == s])
  nincorrectRTs[s] <- sum(sim_dat$button_pressed[sim_dat$correct == 0 &
                                                 sim_dat$RT > 0 &
                                                 sim_dat$ID == s])
  
  for (i in 1:ntrials[s]){
    condition_dum[i, sim_dat$condition[sim_dat$ID == s][i], s] <- 1
    task_dum[i, sim_dat$task_num[sim_dat$ID == s][i], s] <- 1
  }
  for (task in 1:ntasks){
    min_rt[s,task] <- min(sim_dat$RT[sim_dat$RT > 0 & sim_dat$ID == s & sim_dat$task_num == task])
  }
}

A_T <- chol(covar_matrix) # Cholesky decomposition

A <- t(A_T)

data <- list(nagents = nagents,
             ntrials = ntrials,
             maxntrials = maxntrials,
             nconditions = nconditions,
             ntasks = ntasks,
             target_present = target_present,
             button_pressed = button_pressed,
             correct = correct,
             RT = RT,
             falsealarm = falsealarm,
             incorrectRTs_present = incorrectRTs_present,
             ncorrectRTs = ncorrectRTs,
             nincorrectRTs = nincorrectRTs,
             condition_dum = condition_dum,
             task_dum = task_dum,
             min_rt = min_rt,
             A = A,
             
                a_M_prior_m = a_M_prior_m,
                a_M_prior_sd = a_M_prior_sd,
                a_SD_prior_m = a_SD_prior_m,
                a_SD_prior_sd = a_SD_prior_sd,
                b_M_prior_m = b_M_prior_m,
                b_M_prior_sd = b_M_prior_sd,
                b_SD_prior_m = b_SD_prior_m,
                b_SD_prior_sd = b_SD_prior_sd,
                v_M_prior_m = v_M_prior_m,
                v_M_prior_sd = v_M_prior_sd,
                v_SD_prior_m = v_SD_prior_m,
                v_SD_prior_sd = v_SD_prior_sd,
                t_M_prior_m = t_M_prior_m,
                t_M_prior_sd = t_M_prior_sd,
                t_SD_prior_m = t_SD_prior_m,
                t_SD_prior_sd = t_SD_prior_sd,
                
                d_prior_m = d_prior_m,
                d_prior_sd = d_prior_sd,
                w_prior_m = w_prior_m,
                w_prior_sd = w_prior_sd,
                FA_prior_m = FA_prior_m
             )

```




-- Fit model
```{r}
samples <- TGM_mod$sample(
  data = data,
  seed = 123,
  chains = 3,
  parallel_chains = 3,
  iter_warmup = 1000,
  iter_sampling = 3000,
  refresh = 10,
  max_treedepth = 10,
  adapt_delta = 0.99
)
```



Load draws data and true parameter values
```{r}
filenames <- list.files(path = "C:/Users/andre/OneDrive - Aarhus universitet/Cognitive Science/Kandidat/Speciale/Analysis/Task_general_model/draws_and_true_params", pattern = "draws_trim_TGM_fixed_d_and_SD_v3_2025-03-10_125332.675184_agent_\\d+_init0.csv")

draws_df <- data.frame()

for (filename in filenames) {
  single_agent_draws <- read.csv(paste0("draws_and_true_params/", filename))
  draws_df <- rbind(draws_df, single_agent_draws)
}

true_params <- read.csv("draws_and_true_params/TGM_fixed_d_and_SD_true_params_2025-03-10_125332.675184.csv")
```

Load Simulated data
```{r}
sim_dat <- read.csv("TGM_fixed_d_and_SD_sim_dat_2025-03-10_125332.675184.csv")

d <- array(c(0.5,2,4,
             0.1,NA,NA,
             1,NA,NA), dim = c(ntasks, max(nconditions_pr_task)))
d_vec <- array(d, dim = 9)
d_vec <- d_vec[!is.na(d_vec)]
```


Inspect draws with PP-checks

```{r}
source("C:/Users/andre/OneDrive - Aarhus universitet/Cognitive Science/Kandidat/Speciale/Analysis/visualization_functions/wiener_ppcheck_v2.R")
```

Look at first agent
```{r}
correct_RTs <- sim_dat$RT[sim_dat$correct == 1 & sim_dat$button_pressed == 1 & sim_dat$ID == 1]
ntrials_pr_condition <- c(150,150,150,360,300)
nconditions <- sum(nconditions_pr_task)

wiener_ppcheck(RT_data = correct_RTs,
               ntrials_pr_condition = ntrials_pr_condition, 
               a_samples = draws_df$a_M.1.[draws_df$ID == 1],
               b_samples = draws_df$b_M.1.[draws_df$ID == 1],
               v_samples = draws_df$v_M.1.[draws_df$ID == 1],
               t_samples = draws_df$t_M.1.[draws_df$ID == 1],
               w_samples = draws_df$w.1.[draws_df$ID == 1],
               nconditions = 5,
               d = d_vec
               )

wiener_ppcheck(RT_data = correct_RTs,
               ntrials_pr_condition = ntrials_pr_condition, 
               a_samples = draws_df$a_M_prior[draws_df$ID == 1],
               b_samples = draws_df$b_M_prior[draws_df$ID == 1],
               v_samples = draws_df$v_M_prior[draws_df$ID == 1],
               t_samples = draws_df$t_M_prior[draws_df$ID == 1],
               w_samples = draws_df$w_prior[draws_df$ID == 1],
               nconditions = 5,
               d = d_vec, 
               prior_only = TRUE
               )


  

```

PP checks of hit rate and com. rate
```{r}
theta <- function(a, b, v, w, d, FA, target_present) {
  if (target_present == 1){
    bias <- b
  } else {
    bias <- 1-b
  }
  EEA_given_d <- v - (0.2 * d)
  EEA_given_d <- ifelse(EEA_given_d < 0, 0, EEA_given_d)
  EEA <- EEA_given_d - FA
  caut <- a + (0.2 * w * d)
  
  thet <- 1-( (1 - exp(-2*EEA*caut*(1-bias))) / (exp(2*EEA*caut*bias) - exp(-2*EEA*caut*(1-bias))) )
  thet <- ifelse(is.nan(thet), bias, thet)
  return(thet)
}


```

```{r}
draws_df1 <- draws_df %>% filter(ID == 1)
n_conditions <- 5
ntargets_pr_condition <- c(30,30,30,324,24)
```


hit rate
```{r}
theta_prior <- array(NA, dim = c(12000, 5))

for (c in 1:5) {
  for (i in 1:12000){}
    theta_prior[,c] <- theta(draws_df1$a_M_prior,
                                draws_df1$b_M_prior,
                                draws_df1$v_M_prior,
                                draws_df1$w_prior,
                                d = d_vec[c],
                                FA = 0,
                                target_present = 1)
}

# sample_idx <- floor(runif(3000, min = 1, max = nrow(draws_df1)))
# 
# hit_rate_prior <- array(NA, dim = c(3000, n_conditions))
# 
# for (i in 1:length(sample_idx)){
#   idx <- sample_idx[i]
#   
#   for (c in 1:n_conditions){
#     temp <- rbinom(1, ntargets_pr_condition[c], theta_prior[idx,c]) / ntargets_pr_condition[c]
#     hit_rate_prior[i,c] <- temp
#   }
# }

hit_rate_prior_df <- data.frame(theta_prior)

colnames(hit_rate_prior_df) <- c("CPT-IP cond. 1", "CPT-IP cond. 2", "CPT-IP cond. 3",
                                 "Conners'", "RVP")

hit_rate_prior_df <- hit_rate_prior_df %>% pivot_longer(names_to = "Condition", cols = everything())

cond_order <- c("CPT-IP cond. 1", "CPT-IP cond. 2", "CPT-IP cond. 3",
                                 "Conners'", "RVP")

hit_rate_prior_df <- hit_rate_prior_df %>% 
  mutate(Condition = factor(Condition, levels = cond_order)) %>% 
  arrange(Condition)


hit_rate_prior_df %>% 
  ggplot() +
  geom_density(aes(value, color = Condition)) +
  theme_minimal() +
  labs(title = "Prior Hit Rate predictions",
       x = "Hit Rate",
       y = "Density") +
  theme(text = element_text(size = 14, family = "serif"))
```


```{r}
### Posterior
hit_rate_post <- array(NA, dim = c(12000, 5))


for (c in 1:5) {
  hit_rate_post[,c] <- theta(draws_df1$a_M.1.,
                              draws_df1$b_M.1.,
                              draws_df1$v_M.1.,
                              draws_df1$w.1.,
                              d = d_vec[c],
                              FA = 0,
                              target_present = 1)
}

hit_rate_post_df <- data.frame(hit_rate_post)

colnames(hit_rate_post_df) <- c("CPT-IP cond. 1", "CPT-IP cond. 2", "CPT-IP cond. 3",
                                 "Conners'", "RVP")

hit_rate_post_df <- hit_rate_post_df %>% pivot_longer(names_to = "Condition", cols = everything())

hit_rate_post_df <- hit_rate_post_df %>% 
  mutate(Condition = factor(Condition, levels = cond_order)) %>% 
  arrange(Condition)

hit_rate_post_df$cond_num <- str_sub(hit_rate_post_df$Condition, -1, -1)

true_hitrate <- data.frame("cond_num" = c(1,2,3,"'","P"), "true_hitrate" = NA)
for (c in 1:n_conditions){
  true_hitrate$true_hitrate[c] <- sum(sim_dat$button_pressed[sim_dat$target_present == 1 &
                                                  sim_dat$ID == 1 &
                                                  sim_dat$condition == c]) / ntargets_pr_condition[c]
}
true_hitrate$true_hitrate[2] <- true_hitrate$true_hitrate[2] + 0.003

hit_rate_post_df <- merge(hit_rate_post_df, true_hitrate, by = "cond_num")

hit_rate_post_df %>% 
  ggplot() +
  geom_density(aes(value, color = Condition)) +
  geom_vline(aes(xintercept = true_hitrate, color = Condition)) +
  theme_minimal() +
  labs(title = "Posterior Hit Rate predictions",
       x = "Hit Rate",
       y = "Density") +
  guides(color = guide_legend(title = "Condition")) +
  theme(text = element_text(size = 14, family = "serif"))
  

```


com rate

```{r}
ndistractors_pr_condition <- ntrials_pr_condition - ntargets_pr_condition
com_rate_prior <- array(NA, dim = c(12000, 5))

for (c in 1:5) {
  com_rate_prior[,c] <- 1 - theta(draws_df1$a_M_prior,
                              draws_df1$b_M_prior,
                              draws_df1$v_M_prior,
                              draws_df1$w_prior,
                              d = d_vec[c],
                              FA = 0,
                              target_present = 0)
}

com_rate_post <- array(NA, dim = c(12000, 5))

for (c in 1:5) {
  com_rate_post[,c] <- 1 - theta(draws_df1$a_M.1.,
                              draws_df1$b_M.1.,
                              draws_df1$v_M.1.,
                              draws_df1$w.1.,
                              d = d_vec[c],
                              FA = 0,
                              target_present = 0)
}

com_rate_prior_df <- data.frame(com_rate_prior)
com_rate_post_df <- data.frame(com_rate_post)

colnames(com_rate_prior_df) <- c("CPT-IP cond. 1", "CPT-IP cond. 2", "CPT-IP cond. 3",
                                 "Conners'", "RVP")
colnames(com_rate_post_df) <- c("CPT-IP cond. 1", "CPT-IP cond. 2", "CPT-IP cond. 3",
                                 "Conners'", "RVP")

com_rate_prior_df <- com_rate_prior_df %>% pivot_longer(names_to = "Condition", cols = everything())
com_rate_post_df <- com_rate_post_df %>% pivot_longer(names_to = "Condition", cols = everything())

cond_order <- c("CPT-IP cond. 1", "CPT-IP cond. 2", "CPT-IP cond. 3",
                                 "Conners'", "RVP")

com_rate_prior_df <- com_rate_prior_df %>% 
  mutate(Condition = factor(Condition, levels = cond_order)) %>% 
  arrange(Condition)

com_rate_post_df <- com_rate_post_df %>% 
  mutate(Condition = factor(Condition, levels = cond_order)) %>% 
  arrange(Condition)


com_rate_prior_df %>% 
  ggplot() +
  geom_density(aes(value, color = Condition)) +
  theme_minimal() +
  labs(title = "Prior Com. Rate predictions",
       x = "Com. Rate",
       y = "Density") +
  theme(text = element_text(size = 14, family = "serif"))


com_rate_post_df$cond_num <- str_sub(com_rate_post_df$Condition, -1, -1)

true_comrate <- data.frame("cond_num" = c(1,2,3,"'","P"), "true_comrate" = NA)
for (c in 1:n_conditions){
  true_comrate$true_comrate[c] <- sum(sim_dat$button_pressed[sim_dat$target_present == 0 &
                                                  sim_dat$ID == 1 &
                                                  sim_dat$condition == c]) / ndistractors_pr_condition[c]
}
#true_comrate$true_comrate[2] <- true_comrate$true_comrate[2] + 0.003

com_rate_post_df <- merge(com_rate_post_df, true_comrate, by = "cond_num")


com_rate_post_df %>% 
  ggplot() +
  geom_density(aes(value, color = Condition)) +
  geom_vline(aes(xintercept = true_comrate, color = Condition)) +
  theme_minimal() +
  labs(title = "Posterior Com. Rate predictions",
       x = "Com. Rate",
       y = "Density") +
  guides(color = guide_legend(title = "Condition")) +
  theme(text = element_text(size = 14, family = "serif"))
```




Wrangle data for visualization purposes
```{r Data wrangling}
# Turn to long format
draws <- draws_df %>%
  dplyr::select(-starts_with("d"), -starts_with("log_d")) %>%
  pivot_longer(cols = starts_with(c("log", "a", "v", "t", "FA", "cont", "w", "b")),
               values_to = "value", names_to = "varname") %>% 
  mutate(#param = str_sub(str_extract(varname, "\\w+\\_?\\w+(?>=.\\d+)"), 1, -2))
    param = sub("[.]+\\d+[.]?\\d*[.]?", "", varname),
    # ID = str_extract(str_extract(varname, "\\d+[.]\\d*"), "\\d+"),
    task = str_sub(str_extract(str_extract(varname, "\\d+[.]\\d*"), "[.]\\d+"), start = 2),
    type = ifelse(!is.na(str_extract(varname, "prior")), "Prior", "Posterior"),
    ) %>% 
  dplyr::select(-varname)


draws <- draws %>% filter(type != "Prior")

```


Summarize the draws and plot against true param values

```{r Summarize draws}
recov_summa <- draws %>% filter(param %in% c("a_M", "b_M", "v_M", "t_M", "w")) %>%
  group_by(ID, param) %>%
  summarize(infer_mean = as.numeric(mean(value))) %>%
  pivot_wider(names_from = param, values_from = infer_mean)

true_params_temp <- true_params %>% dplyr::select(s, a_m, b_m, v_m, t_m, w)
colnames(true_params_temp) <- c("ID", "true_a_M", "true_b_M","true_v_M", "true_t_M", "true_w")

recov_summa <- merge(recov_summa, true_params_temp, by = "ID")

recov_summa <- recov_summa %>% mutate(
  a_M = as.numeric(a_M),
  b_M = as.numeric(b_M),
  v_M = as.numeric(v_M),
  t_M = as.numeric(t_M)
)

```


Preservation of ranking, Fit ordinal regression

```{r}
library(ordinal)
# Get ranking of the true parameters
true_params$rank_a <- rank(true_params$a_m)
true_params$rank_b <- rank(true_params$b_m)
true_params$rank_v <- rank(true_params$v_m)
true_params$rank_t <- rank(true_params$t_m)
true_params$rank_w <- rank(true_params$w)
ranking_d <- true_params %>% dplyr::select(s, starts_with("rank"))
ranking_d <- ranking_d %>% rename("ID" = s)

draws_df <- merge(draws_df, ranking_d, by = "ID") # merge rankings with the draws


draws_df$rank_a <- as.factor(draws_df$rank_a)
draws_df$rank_b <- as.factor(draws_df$rank_b)
draws_df$rank_v <- as.factor(draws_df$rank_v)
draws_df$rank_t <- as.factor(draws_df$rank_t)
draws_df$rank_w <- as.factor(draws_df$rank_w)
#draws_df$rank_FA <- as.factor(draws_df$rank_FA)

draws_df <- draws_df %>% 
  mutate(
    a_M_z = z(a_M.1.),
    b_M_z = z(b_M.1.),
    v_M_z = z(v_M.1.),
    t_M_z = z(t_M.1.),
    w_z = z(w.1.)
  )


# Fit models for each param

m_a <- clm(rank_a ~ a_M_z, data = draws_df)

m_b <- clm(rank_b ~ b_M_z, data = draws_df)

m_v <- clm(rank_v ~ v_M_z, data = draws_df)

m_t <- clm(rank_t ~ t_M_z, data = draws_df)

m_w <- clm(rank_w ~ w_z, data = draws_df)

#m_FA <- clm(rank_FA ~ FA, data = draws_df)


m_a$coefficients["a_M_z"]
m_b$coefficients["b_M_z"]
m_v$coefficients["v_M_z"]
m_t$coefficients["t_M_z"]
m_w$coefficients["w_z"]
#m_FA$coefficients["FA"]


summary(m_a)
summary(m_b)
summary(m_v)
summary(m_t)
summary(m_w)
#summary(m_FA)
```

Mean of absolute errors

```{r}
nagents <- 30
niter <- 12000


# a
infer_a <- array(draws_df$a_M.1., dim = c(niter, nagents))
infer_a <- t(infer_a) # transpose so that we have a row for each agent and column for each sample
a_abs_err <- array(NA, dim = dim(infer_a))
for (i in 1:nagents){
  a_abs_err[i,] <- abs(infer_a[i,] - true_params$a_m[i])
}
a_mean_abs_err <- colMeans(a_abs_err)
#plot(density(a_mean_abs_err))


# b
infer_b <- array(draws_df$b_M.1., dim = c(niter, nagents))
infer_b <- t(infer_b) # transpose so that we have a row for each agent and column for each sample
b_abs_err <- array(NA, dim = dim(infer_b))
for (i in 1:nagents){
  b_abs_err[i,] <- abs(infer_b[i,] - true_params$b_m[i])
}
b_mean_abs_err <- colMeans(b_abs_err)
#plot(density(b_mean_abs_err))



# v
infer_v <- array(draws_df$v_M.1., dim = c(niter, nagents))
infer_v <- t(infer_v) # transpose so that we have a row for each agent and column for each sample
v_abs_err <- array(NA, dim = dim(infer_v))
for (i in 1:nagents){
  v_abs_err[i,] <- abs(infer_v[i,] - true_params$v_m[i])
}
v_mean_abs_err <- colMeans(v_abs_err)
#plot(density(v_mean_abs_err))


# t
infer_t <- array(draws_df$t_M.1., dim = c(niter, nagents))
infer_t <- t(infer_t) # transpose so that we have a row for each agent and column for each sample
t_abs_err <- array(NA, dim = dim(infer_t))
for (i in 1:nagents){
  t_abs_err[i,] <- abs(infer_t[i,] - true_params$t_m[i])
}
t_mean_abs_err <- colMeans(t_abs_err)
#plot(density(t_mean_abs_err))


# w
infer_w <- array(draws_df$w.1., dim = c(niter, nagents))
infer_w <- t(infer_w) # transpose so that we have a row for each agent and column for each sample
w_abs_err <- array(NA, dim = dim(infer_w))
for (i in 1:nagents){
  w_abs_err[i,] <- abs(infer_w[i,] - true_params$w[i])
}
w_mean_abs_err <- colMeans(w_abs_err)
#plot(density(w_mean_abs_err))




mean_abs_err_df <- data.frame(a_mean_abs_err, b_mean_abs_err, v_mean_abs_err, t_mean_abs_err, w_mean_abs_err)

mean_abs_err_df %>% ggplot() +
  geom_density(aes(a_mean_abs_err)) +
  theme_minimal()
mean_abs_err_df %>% ggplot() +
  geom_density(aes(b_mean_abs_err)) +
  theme_minimal()
mean_abs_err_df %>% ggplot() +
  geom_density(aes(v_mean_abs_err)) +
  theme_minimal()
mean_abs_err_df %>% ggplot() +
  geom_density(aes(t_mean_abs_err)) +
  theme_minimal()
mean_abs_err_df %>% ggplot() +
  geom_density(aes(w_mean_abs_err)) +
  theme_minimal()



```



Inspect effect of w
```{r}
sim_dat <- data.frame()
nsims <- 100
w <- runif(nsims, 0.3, 3)
for (s in 1:nsims){
  
  CPT_IP_sim <- CPT_IP_w_diff_and_caut_wiener_sim_f(item_type = CPT_IP_stimuli$stim_type,
                                                    v = 1.2, a = 1.2,
                                                    b = 0.5, tau = 0.2,
                                                    d = c(5,10,20), FA = -1, w = w[s])
  
  CPT_IP_sim$ID <- s
  CPT_IP_sim$task <- "CPT-IP"
  
  sim_dat <- rbind(sim_dat, CPT_IP_sim)
  
}
HitRate <- sim_dat %>% filter(target_present == 1) %>% group_by(condition, ID) %>% summarise(hitrate = sum(correct)/90, mean_RT = mean(RT)) %>% mutate(w = w)

HitRate %>% ggplot() +
  geom_point(aes(x=w, y=hitrate)) +
  facet_wrap(.~condition)

HitRate %>% ggplot() +
  geom_point(aes(x=w, y=mean_RT)) +
  facet_wrap(.~condition)

```


